Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-29 acl.2016/acl2016.tex
acl paper

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo into next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo into next stack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}

>>>>

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next ministack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
Table~\ref{tab:stack-configuration} present the decoding time (with 32 threads) for each stack configuration, and the average model on the held out test set.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|p{17mm}|p{17mm}|} \hline
			& Decoding \newline Time(secs)	& Avg model \newline score \\ \hline
Coverage cardinality  	& 186 	& -8.59922 \\
Coverage 		& ??? 	& ??? \\ 
Coverage \& end pos	& 196	& -8.59922 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time and average model scores for different stack configurations}
\label{tab:stack-configuration}
\end{table}

The algorithms in Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack} and ~\ref{algo:Hypothesis Expansion with Sorted Stack} describes the standard phrase-based decoding algorithm, however, the stack configuration issues are the same in the cube-pruning algorithm. Furthermore, the cube-pruning algorithm also contain a priority queue which is attached to coverage cardinality in Moses, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE initialize $queue_{|C|}$
\FOR{1 to pop-limit}
  \STATE get best $item$ in $queue_{|C|}$
  \STATE create new hypo from $item$
  \STATE add new hypo to new $stack_{|C|}$
  \STATE create next $items$
  \STATE add new $items$ to $queue_{|C|}$
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Cube Pruning with Unsorted Stack}
\label{algo:Cube Pruning with Unsorted Stack}
\end{figure}
We experiment with changing the queue, $queue_{|C|}$, by having separate queues for each (1) unique coverage $queue_{C}$, and each (2) unique coverage and end position $queue_{C, e}$. The stack configuration stayed constant.
